Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-06-01 draft.tex
add new, simplified exposition at start of section 2.2

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of periods $t=1,2,\ldots$, with play proceeding until an absorbing state is reached.

Importantly, the payoffs for what we term the `inside actors'---the secessionists and the home government---are modeled as state variables. The status quo payoffs for the secessionists are special in that the transition of this state variable from one period to the next involves an automatic reduction by $\mu$. The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs to the secessionists from the status quo evolve according to the law of motion $Q_s^{t} = Q_s^{t-1} - \mu + R_p^t - R_c^t$ where $R_p^t$ is the investment of the patron and $R_c^t$ is the investment of the international community in period $t$.\footnote{Here we anticipate a bit the incentives of the patron and international community to sign the impact of contributions: the patron will want to increase the value of the status quo to the secessionists, while the international community could only desire to reduce this value.}

>>>>

The payoff functions and all parameters, including probabilities in the war lottery, are common knowledge for all players, and actions are immediately observed by all players at the time they occur. There are an infinite number of discrete periods $t=1,2,\ldots$, with play proceeding until an absorbing state is reached.

Within each period, there is first an investment stage in which first the patron and then the international community each make decisions about how much to invest in altering the payoffs of the `inside actors'---the secessionists and the home government. Then, the inside actors play a ``conflict stage game'' in which they simultaneously choose whether to cede the issue of status, fight, or maintain the status quo.

The payoffs at the end of a period are determined by these actions and six state variables, which keep track of the per-period value of the status quo ($Q_s^t$ and $Q_g^t$), losing the issue of recognition ($L_s^t$ and $L_g^t$) and winning the issue of recognition ($W_s^t$ and $W_g^t$) to the secessionists and government respectively. The game continues into the next period if the inside players selected (status quo, status quo) or (cede, cede). Otherwise, the game ends in an absorbing state as described below.

The status quo payoffs for the secessionists are special in that the transition of this state variable from one period to the next involves an automatic reduction by $\mu$. The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction. As the economy in the secessionist region deteriorates, so does the standard of living for the secessionists. Therefore, the payoffs to the secessionists from the status quo evolve according to the law of motion $Q_s^{t} = Q_s^{t-1} - \mu + R_p^t - R_c^t$ where $R_p^t$ is the investment of the patron and $R_c^t$ is the investment of the international community in period $t$.\footnote{Here we anticipate a bit the incentives of the patron and international community to sign the impact of contributions: the patron will want to increase the value of the status quo to the secessionists, while the international community could only desire to reduce this value.}
